---
title: "Trains"
format: html
execute:
  echo: false
---

## Summary

Attitudes toward immigration, as reported on standardized survey scales, can shift in response to brief social exposure to speakers of another language. Using data from Ryan Enos's January 2012 platform-randomized field experiment on the MBTA Commuter Rail, we investigate the average causal effect of exposure to Spanish-speaking confederates on commuters' post-experiment immigration attitude scores. A key weakness of this model is that it relies on a narrow, non-randomly-selected sample of 115 Boston-area commuters from a single two-week window in 2012, meaning the confidence interval — though statistically valid for that sample — likely understates the true uncertainty involved in generalizing the estimated effect to any broader or more current population.

```{r}
#| label: setup
#| include: false
#| message: false
library(tidyverse)
library(primer.data)
library(broom)
```

```{r}
#| echo: true
library(primer.data)
library(tidyverse)

data("trains", package = "primer.data")

ggplot(trains, aes(x = treatment, y = att_end)) +
  geom_jitter(width = 0.1, alpha = 0.7, color = "steelblue") +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4, color = "red") +
  labs(
    title = "Individual att_end values by treatment group",
    subtitle = "Each point is one person; the red point shows the group mean",
    x = "Treatment",
    y = "att_end",
    caption = "Data from the trains tibble"
  ) +
  theme_minimal()
```

```{r}
glimpse(trains)
```

